Approximation as Differentiation

### 2025-07-02 main/approx-as-tangents.tex
Citations on gradient descent.

Computing the forward and backward derivatives of smooth functions $f$ has many applications of practical interest. For example, computation of the reverse derivative is of central interest in Machine Learning by Gradient Descent, the main technique used to train Deep Neural Networks. \bob{need a citation here}.

>>>>

Computing the forward and backward derivatives of smooth functions $f$ has many applications of practical interest. For example, computation of the reverse derivative is of central interest in machine learning by gradient descent, the main technique used to train deep neural networks~\cite{rumelhart88,goodfellow16}.
